A robust framework for variable extrusion width concentric toolpath generation

### 2019-08-05 6_validation.tex
move Moessen method to before Constant
The Moessen method only has a small advantage over the naive method.
emulate related work correctly
describe validation setup

\paragraph{Constant bead count}
Emulates \cite{Ding2016a}

\begin{align*}
b(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\paragraph{Only outer bead}
Emulates \cite{Moesen2011}

@@

\subsection{Computational analysis}
\paragraph{Accuracy}
Render toolpaths and calculate amount of overfilling and amount of underfilling.

\paragraph{Printability}
Define some function to determine printability $0<P<1$, 
then define a loss function $L = 1/P$.
Evaluate average loss divided by total toolpath length.

\old{Visualize thickness of beads as color.}

Show results for different settings.

\old{Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.}

>>>>

\paragraph{Only outer bead}
Emulates \cite{Moesen2011}. We don't reduce line segments in 3-way intersections.

\paragraph{Constant bead count}
Emulates \cite{Ding2016a}. We unmark all outer segments.

\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
b(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

@@

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The naive method was implemented using the state-of-the-art polygon offset library called Clipper. \cite{johnson2014clipper}

\paragraph{Accuracy}
In order to estimate the overfill and underfill we need to accurately calculate the area covered by a single extrusion path.
If we would simply use a isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment we would get strange artifacts at corners in the toolpath.
We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.
For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
See \cref{segment_visualization}.

\begin{figure}
\centering
\setlength{\figwidth}{.25\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_blocky.pdf}
\caption{Blocky}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded.pdf}
\caption{Rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded_excluded.pdf}
\caption{Excluded}
\end{subfigure}
\caption{
Extruded area of two extrusion toolpath segments.
Red areas signify doubly extruded areas.
}
\label{segment_visualization}
\end{figure}

We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then takign the difference from the original outline shape.
In order to deal with rounding errors we perform a morpholocial close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.

The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
These tripple extrusion areas count double toward the total amount of overfill.
The resulting overfill and underfill areas are visualzied for the different toolpath strategies in \cref{visualized_accuracy}.

\todo{Visualize results in tables and/or graphs.}

\paragraph{Manufacturability}
Depending on the hardware configuration some bead widths are difficult to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
We visualize the bead widths reslting from the different strategies in an exaggerated manner in \cref{visualized_accuracy}.
